

# Loading and preparing data

```{r}
act <- read.csv("~/Documentos Ed/R Directory/data/activity.csv")
str(act)

act <- read.csv("~/Documentos Ed/R Directory/data/activity.csv",colClasses=c("numeric","Date","numeric"))
str(act)
```

#What is mean total number of steps taken per day?

```{r}
sum_by_date <- tapply(act$steps,act$date,sum,na.rm=TRUE)
hist(sum_by_date,col=heat.colors(8),xlab="Total Steps by Date",main="Histogram of Total Steps by Date")
```

The mean and the median for the total number of steps per day is located below.

```{r}
mean(sum_by_date)

median(sum_by_date)
```

#What is the average daily activity pattern?

I use tapply() calculate the mean of the steps per interval. Next, the data is implemented in the time series plot below.

```{r}
mean_by_int <- tapply(act$steps,act$interval,mean,na.rm=TRUE)
plot(row.names(mean_by_int),mean_by_int,type="l",xlab="Time intervals (in minutes)",ylab="Average of Total Steps",main="Time Series Plot of the Average of Total Steps in a Day")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps? The answer is time interval 835. 

```{r}
x <- max(mean_by_int)
match(x,mean_by_int)

mean_by_int[104]
```

#Imputing missing values

```{r}
sum(is.na(act))

act_na <- act[is.na(act),]
act_no_na <- act[complete.cases(act),]
act_na$steps <- as.numeric(mean_by_int)
new_act <- rbind(act_na,act_no_na)
new_act <- new_act[order(new_act[,2],new_act[,3]),]
```
Histogram

```{r}
new_sum_by_date <- tapply(new_act$steps,new_act$date,sum)
hist(new_sum_by_date,col=terrain.colors(8),xlab="Total Steps by Date",main="Adjusted Histogram of Total Steps by Date (no missing values)")
```

